\documentclass[12pt, a4paper]{eon-resume}

\name{abhishekh}{reddy munnangi}
\academiclvl{graduate student}{robotics}
\email{helloarm@pm.me}
\website{github.com/areddy42}

\begin{document}

\begin{section}{education}

  \begin{school}
    {M.Eng in Robotics}
    {University of Maryland, College Park}
    {Aug 2022 - Present}
    
    \item Finished second semester with 3.11 GPA
    
  \end{school}

  \begin{school}
    {B.Tech in Mechatronics Engineering}
    {Ajeenkya DY Patil University, Pune}
    {Aug 2018 - May 2022}

    \item Graduated with 7.87/10 CGPA

  \end{school}

\end{section}

\begin{section}{skills}

  \skills{Computer Languages}{C++, Python and MATLAB} \\
  \skills{Softwares}{KiCAD, Fusion 360, Solidworks, STM32CubeMX} \\
  \skills{Utilities}{Linux Shell, Docker}
  
\end{section}

\begin{section}{experience}

  \begin{work}
    {Software Team Member}
    {Terraformers URC}
    {}
    {Apr 2023 - Present}

    \item Developing software for the rover and its manipulator for the 2024 University Rover Challenge.
    \item Writing a URDF description file for the manipulator to integrate with ROS ecosystem.
    \item Setting up communication between an STM32 Nucleo Board and a single-board computer using micro-ROS.
  
  \end{work}

  \begin{work}
    {Robotics Engineer Intern}
    {iTrontik Smart Systems}
    {}
    {May 2021 - Apr 2022}

    \item Worked on the hardware of a nano class (less than 250g) quadcopter drone.
    \item Sized the components of a quadcopter drive system and selected suitable off-the-shelf parts.
    \item Designed and 3D-printed a sturdy quadcopter frame for prototyping using Fusion 360.
    \item Created circuit schematic and a 2-layer PCB design for USB charger board of the drone battery pack.
  
  \end{work}

\end{section}

\begin{section}{projects}
  
  \begin{project}
    {Mint Flight Controller Board}
    {personal project}
    {Oct 2020 - May 2021}

    \item Designed a miniature flight controller board for quadcopter drones based on STM32H7 microcontroller.
    \item Created the circuit schematic and a 4-layer PCB design in KiCAD.
    \item Ported ArduPilot flight control software to the new board by modifying the target hwdef file.
  
  \end{project}

  \begin{project}
    {Brushless Motor Speed Controller}
    {coursework project}
    {Nov 2019 - Dec 2019}

    \item Built a simple brushless DC motor driver based on 3-phase inverter circuit.
    \item Programmed an Arduino Nano board to signal the MOSFETs for driving the brushless motor.
    \item Created the circuit schematic in KiCAD and hand-soldered the components on a perfboard.
  
  \end{project}

  \begin{project}
    {Hybrid Landing Gear}
    {coursework project}
    {Jan 2019 - May 2019}

    \item Developed a landing gear system that also functions as a gripper for multicopter drones.
    \item Created the design in Fusion 360 that was further 3D-printed.
    \item Written code for an Arduino Nano board to read the PWM input from a radio receiver and control the servos.
  
  \end{project}

  \begin{project}
    {Justbot Manipulator}
    {coursework project}
    {Nov 2022 - Dec 2022}

    \item Created a 6 DOF manipulator design in Solidworks, built a ROS package, and simulated it using Gazebo and RViz.
    \item Wrote a Python publisher node to compute the inverse kinematics of the robot using numpy and rospy.
  
  \end{project}

\end{section}

\end{document}