\begin{section}{experience}

  \begin{work}
    {Teaching Assistant}
    {Institute for Systems Research}
    {UMD}
    {Aug 2023 - Present}

    \item Served as a Teaching Assistant for a Robotics Laboratory Course:
          ENEE467 in Fall '23 semester. Interacted with students from
          diverse engineering backgrounds.

    \item Instructed and guided students in interdisciplinary lab exercises
          including writing a roscpp node to draw shapes with a real UR3e
          robotic arm and developing a line follower program for the TI Robotic
          Systems Learning Kit.

    % TODO: Mention about fixing that MoveIt wrapper package
    \item Delivered a hotfix for the C++ wrapper library based on MoveIt!
          API used during the course. This significantly improved execution
          success rate of the code written by students when using the Cartesian
          planner to move the robotic arm.

    \item Maintained the instructions and documentation for the lab exercises
          written in Markdown on GitHub Wiki.

    \item Assisted with debugging C++ and Embedded C code written by students
          for the lab exercies.

    % \item Assisted students with setting up GPIOs, SysTick timer, General
    %       purpose timer and PWM signal generation on TI-MSP432 Launchpad board.

    % \item Supported students in debugging Embedded C code by identifying
    %       incorrect register values and program flow errors.

  \end{work}

  % \begin{work}
  %   {Software Team Member}
  %   {Terraformers URC}
  %   {}
  %   {Apr 2023 - Present}

  %   \item Developing software for the rover and its robotic arm for the 2024
  %         University Rover Challenge.

  %   \item Creating a description package for the 6DOF robotic arm design to
  %         integrate with the ROS ecosystem.

  %   \item Leveraging micro-ROS to setup a node on STM32 Nucleo Board to
  %         communicate with a single-board computer.

  % \end{work}

  \begin{work}
    {Robotics Engineer Intern}
    {iTrontik Smart Systems}
    {Pune}
    {May 2021 - Apr 2022}

    \item Worked on the hardware of a nano class (less than 250g) quadcopter
          drone.

    \item Sized the components of the quadcopter drive system for hover flight
          time and selected suitable off-the-shelf parts.

    \item Designed and 3D-printed a sturdy quadcopter frame for prototyping
          using Fusion 360 in three iterations. The frame was able to sustain
          multiple hard and crash landings during testing.

    \item Created circuit schematic and 2-layer PCB design for a USB-C charger
          board that integrates into the drone battery pack. This reduced the
          need for an external charger.

  \end{work}

\end{section}
