\begin{section}{projects}
  
  \begin{project}
    {Mint Flight Controller Board}
    {personal project}
    {Oct 2020 - May 2021}

    \item Designed a miniature flight controller board for quadcopter drones based on STM32H7 microcontroller.
    \item Created the circuit schematic and a 4-layer PCB design in KiCAD.
    \item The resulting board sizes 80 percent smaller than Pixhawk 4 while retaining most functionality.
  
  \end{project}

  \begin{project}
    {Brushless Motor Speed Controller}
    {coursework project}
    {Nov 2019 - Dec 2019}

    \item Built a 3-phase inverter circuit using MOSFETs, gate drivers and op-amps to drive a brushless motor.
    \item Created the circuit schematic in KiCAD and hand-soldered the components on a perfboard.
  
  \end{project}

  \begin{project}
    {Hybrid Landing Gear}
    {coursework project}
    {Jan 2019 - May 2019}

    \item Developed a landing gear system that also functions as a gripper for multicopter drones.
    \item Created the design in Fusion 360 that was further 3D-printed.
    \item Written code for an Arduino Nano board to read the PWM input from a radio receiver and control the servos.
  
  \end{project}

  \begin{project}
    {Justbot Manipulator}
    {coursework project}
    {Nov 2022 - Dec 2022}

    \item Created a 6 DOF manipulator design in Solidworks, built a ROS package, and simulated it using Gazebo and RViz.
    \item Wrote a Python publisher node to compute the inverse kinematics of the robot using numpy and rospy.
  
  \end{project}

\end{section}